Towards Contract Modules for the Tezos Blockchain

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
contract syntax

  val close
    : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
    -> (Tezos.status, close_errors) Tezos.monad
end
\end{lstlisting}
Listing~\ref{lst:generated-signature} contains an OCaml module
signature as it could be generated from the contract module. The
module \lstinline/Tezos/ supposedly contains types and other low-level
Tezos-specific definitions. Specifically, the type \lstinline/pukh/ for public
key hashes identifies contracts, the type \lstinline/tz/ stands for
Tezos tokens, the type \lstinline/status/ reflects the internal return
status, and \lstinline/monad/ is an internal monad type. The signature
declares a function and an error type for each entrypoint.

The error types mirror the raises clauses. The first argument of each
function is the address of the contract, then an optional argument for
the transaction fee, an argument for passing an amount of tokens
(optional for an unpaid entrypoint), the next argument would be for
the parameter; it is omitted here because its type is
\lstinline/unit/. The return type refers to the specific error type.

@@

  paid entrypoint bid () 
  requires bidding raises "closed" (** auction closed*)
  requires (amount > balance)
  raises "too low" as too_low      (** bid too low *)
end
\end{lstlisting}

@@

\section{Conclusion}
\label{sec:conclusion}
Current blockchains often provide low-level interfaces to interact with smart contracts. These interfaces work with loosely structured data that is impractical for programs to handle. This paper presents outgoing research on programmatic interaction with a smart contract on the Tezos blockchain that could benefit developers of smart contract applications and Oracles. The approach does not provide a general API, but targets each typical smart contract by generating a specialized contract module that provides a typed high-level interface from a smart contract implementation. In doing so, errors in contract calls are explicitly specified in a user-defined data type. A contract call is treated as a function call that grants a typed safe of data in the Ocaml language. In addition, the module can check preconditions before the actual call to reduce the waste of a failed call. As future work, we combine the contract module with our typed API designed to provide a general type-safe programmatic API for the Tezos blockchain.

>>>>

  val close
    : Tezos.pukh -> ?fee:Tezos.tz
    -> (Tezos.status, close_errors) Tezos.monad
end
\end{lstlisting}
Listing~\ref{lst:generated-signature} contains an OCaml module
signature as it could be generated from the contract module. The
module \lstinline/Tezos/ supposedly contains types and other low-level
Tezos-specific definitions. Specifically, the type \lstinline/pukh/ for public
key hashes identifies contracts, the type \lstinline/tz/ stands for
Tezos tokens, the type \lstinline/status/ reflects the internal return
status, and \lstinline/monad/ is an internal monad type. The signature
declares a function and an error type for each entrypoint.

The error types mirror the raises clauses. The first argument of each
function is the address of the contract, then an optional argument for
the transaction fee, an argument for passing an amount of tokens
(only for a paid entrypoint), the next argument would be for
the parameter; it is omitted here because its type is
\lstinline/unit/. The return type refers to the specific error type.

@@

  paid entrypoint bid () 
  requires bidding raises "closed" (** auction closed*)
  requires (amount > balance)
  raises "too low"                 (** bid too low *)
end
\end{lstlisting}

@@

\section{Conclusion}
\label{sec:conclusion}

Current blockchains often provide low-level interfaces to interact with smart contracts. These interfaces work with loosely structured data that is impractical for programs to handle. This paper presents outgoing research on programmatic interaction with a smart contract on the Tezos blockchain that could benefit developers of smart contract applications and Oracles. The approach does not provide a general API, but targets each typical smart contract by generating a specialized contract module that provides a typed high-level interface from a smart contract implementation. In doing so, errors in contract calls are explicitly specified in a user-defined data type. A contract call is treated as a function call that grants a typed safe of data in the Ocaml language. In addition, the module can check preconditions before the actual call to reduce the waste of a failed call. As future work, we combine the contract module with our typed API designed to provide a general type-safe programmatic API for the Tezos blockchain.
